%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


% ___________________________________________________________________________
% CONFIGURATION

% Check awesome-cv.cls for all of the special functions.
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Builtin:
%   awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%   awesome-nephritis, awesome-concrete, awesome-darknight
% Custom:
%   \definecolor{awesome}{HTML}{CA63A8}
\colorlet{awesome}{awesome-red}

% Colors for text
\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{333333}
\definecolor{graytext}{HTML}{5D5D5D}
\definecolor{lighttext}{HTML}{999999}

% Set to false to disable section highlight
\setbool{acvSectionColorHighlight}{true}

% Set the social information separator to a textbar (|)
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% Support for embedding the resume into this cover letter.
\usepackage{pdfpages}


% ___________________________________________________________________________
% PERSONAL INFORMATION

% Available options: circle|rectangle,edge/noedge,left/right
%\photo[rectangle,edge,right]{./profile}

\name{Chris}{Barrick}
\position{Software Engineer{\enskip\cdotp\enskip}Data Scientist}
\address{Athens, GA}

\mobile{(828) 342-2580}
\email{cbarrick1@gmail.com}
\github{cbarrick}
\linkedin{csb1024}

% Supported but unused:
%\homepage{URL}
%\gitlab{gitlab-id}
%\stackoverflow{SO-id}{SO-name}
%\twitter{@twit}
%\skype{skype-id}
%\reddit{reddit-id}
%\extrainfo{extra informations}

% \quote{``Write programs that do one thing and do it well. Write programs to work together."}


% ___________________________________________________________________________
% LETTER INFORMATION
% All of the below lines must be filled out

% The company being applied to
\recipient
  {TCGPlayer.com}
  {~}

% The date on the letter, default is the date of compilation
\letterdate{\today}

% The title of the letter
\lettertitle{Job Application for Data Engineer in Atlanta}

% How the letter is opened
\letteropening{Dear Hiring Manager,}

% How the letter is closed
\letterclosing{Sincerely,}

% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


% ___________________________________________________________________________
% CONTENT

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments (<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Chris Barrick~~~·~~~Cover Letter}
  {\thepage}

% Print the title with above letter informations
\makelettertitle

\begin{cvletter}

\lettersection{About Me}
My name is Chris, and I enjoy gaming nearly as much as engineering. I am a software engineer and data scientist with interests in backend engineering and machine learning, and I love solving tough puzzles. I am naturally curious about every stage of the research and development cycle, and I have experience in frontend, backend, and research. I'm a Unix geek and programming language nerd that's both easy going and a diligent worker. In my free time, I'm a casual Magic player (and Catan, D\&D, ...) and a hobby programmer with a variety of projects on GitHub. I am currently pursuing a masters in Artificial Intelligence at UGA, for which I have completed all course work, and I have previously held multiple internships with companies in and around Atlanta. I am looking for my first full time engineering position.

\lettersection{Why TCGPlayer?}
I was extremely excited when I saw the posting for data engineer in Atlanta. This opportunity has the triple threat of being an engineering position within my area of expertise, being located in my preferred city, and being in a community of my favorite pastimes. For any other opportunity, I'd have to settle for two out of three. Your tech stack seems modern, and your values progressive, both of which are very important to me. This is easily the most exciting opening I've come across.

\lettersection{Why Me?}
This position fits me like a glove. In fact, the challenges of dealing with Magic data is something I've given much thought to in the past. Take card representation for example. Having a well formed representation would be impactful across the board from customer recommendations to price prediction and internal tooling. Using straight card text seems less than ideal because A) much of the text involves symbols outside of standard english, B) that's not very flexible with respect to errata, and C) the game has a formal definition, so a structured representation would more transparently reflect the role cards have within the game. (I would love to learn how TCGPlayer has approached this problem.)

I addition, I am experienced in symbolic programming, and given the formal structure of Magic, it makes perfect sense that TCGPlayer would leverage a symbolic language like Clojure. I have formal experience with Clojure and other LISP dialects, and I am an expert in Prolog (the most popular symbolic language outside of the LISPs). I also have experience working in Spark and Hive for data analysis, and a formal background in SQL. And of course, my master's thesis is in machine learning and data analysis. Not only am I well qualified, I would be excited for the opportunity to interview with TCGPlayer.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
