\cvsection{Projects}
\begin{cventries}

\cventry
{\textnormal{\url{github.com/dsp-uga/hydrus}}}
{Hydrus: Scalable document classification in Spark}
{UGA}
{2018}
{\begin{cvitems}
    \item {Assignment for UGA's Data Science Practicum; prefab algorithms disallowed (e.g. MLlib).}
    \item {Implements Gaussian Naive Bayes and Logistic Regression from low-level RDD operations.}
    \item {Deployed to Google Cloud Dataproc.}
\end{cvitems}}

\cventry
{\textnormal{\url{github.com/cbarrick/evo}}}
{Evo: Parallel genetic algorithms in Go}
{UGA / Hobby}
{2016}
{\begin{cvitems}
    \item {Support for fine-grain parallelism in arbitrary topologies.}
\end{cvitems}}

\cventry
{\textnormal{\url{github.com/cbarrick/Rw-Prolog}}}
{Rw-Prolog: An equational logic programming language}
{UGA}
{2015}
{\begin{cvitems}
    \item {Extends Prolog's unification semantics with support for conditional term-rewriting.}
    \item {Implemented as a meta-interpreter in Prolog.}
    \item {Developed a regular expression library using the language.}
\end{cvitems}}

\cventry
{\textnormal{\url{github.com/cbarrick/plum}}}
{Plum: A logical agent for the board game \textit{Clue}}
{UGA}
{2014}
{\begin{cvitems}
    \item {Communicates with a human operator in natural language (English).}
    \item {Models knowledge as a constraint satisfaction problem with CLP(FD).}
    \item {Uses path-finding and probability estimates to make decisions.}
    \item {Super-human performance.}
\end{cvitems}}

%---------------------------------------------------------
\end{cventries}
